Calendar-based graphics for visualising people's daily schedules

### 2017-07-20 main.tex
spelling

\Abstract{
This paper describes a \code{frame\_calendar} function that organises
and displays temporal data, collected on sub-daily resolution, into a
calendar layout. Calendars are broadly used in society to display
temporal information, and events. The \code{frame\_calendar} utilizes
linear algebra on the date variable to create the layout. It utilizes
the grammar of graphics to create the plots inside each cell, and thus
synchronises neatly with \pkg{ggplot2} graphics. The motivating
application is studying pedestrian behavior, based on counts which are
captured at hourly interval by sensors scattered around the city.
Facetting by the usual features such as day and month, was insufficient
to examine the behavior. Making displays on a monthly calendar format
helps to understand pedestrian patterns relative to events such as work
days, weekends, holidays, and special events. The layout algorithm has
several format variations and options. It is implemented in the R
package \pkg{sugrrants}.
}

@@

\caption[Lag scatterplot in the daily calendar layout]{Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consitent on non-work days than work days.}\label{fig:scatterplot}
\end{figure}
\end{CodeChunk}

>>>>

\Abstract{
This paper describes a \code{frame\_calendar} function that organises
and displays temporal data, collected on sub-daily resolution, into a
calendar layout. Calendars are broadly used in society to display
temporal information, and events. The \code{frame\_calendar} utilizes
linear algebra on the date variable to create the layout. It utilizes
the grammar of graphics to create the plots inside each cell, and thus
synchronises neatly with \pkg{ggplot2} graphics. The motivating
application is studying pedestrian behavior, based on counts which are
captured at hourly interval by sensors scattered around the city.
Facetting by the usual features such as day and month, was insufficient
to examine the behavior. Making displays on a monthly calendar format
helps to understand pedestrian patterns relative to events such as work
days, weekends, holidays, and special events. The layout algorithm has
several format options and variations. It is implemented in the R
package \pkg{sugrrants}.
}

@@

\caption[Lag scatterplot in the daily calendar layout]{Lag scatterplot in the daily calendar layout. Previous hour's count is plotted against each hour's count at Flinders Street Station to demonstrate the autocorrelation at lag 1. The correlation between them is more consistent on non-work days than work days.}\label{fig:scatterplot}
\end{figure}
\end{CodeChunk}
